---
title: "Exploring the Impact of Mental Well-Being on Turnover Intentions in the Early Childcare Workforce: A Structural Equation Modeling Approach with Emphasis on Disability Classroom Demographics"
author: "Astri Doub"
date: "2024-04-29"
output: html_document
---

# Data Cleaning

``` {r loading data and libraries, include=FALSE, cache = FALSE}

library(tidyverse)
library(data.table, include.only = c("rbindlist"))
library(kableExtra)
library(magick)
library(scales)
library(stringr)
library(readxl, include.only = c("read_excel"))
library(effectsize)
library(gtsummary)
library(psych) #for latent variables
library(lavaan) #for CFA and SEM modeling
library(semPlot) #for plotting SEM models

options(scipen = 999)
#setwd("/Users/Astri/Desktop")
knitr::opts_chunk$set(message = FALSE)
data <- read_csv("National Childcare Survey_June - August 2023_ Identified Choice Text Data COPY.csv")
weights <- read_csv("childcare_wave4_crosssection_survey_weights.csv")
data1 = data[-1,]
data2 = data1[-1,]

```

```{r prepare data, include = FALSE, cache = FALSE}

data_clean <- data2 %>%
  # filtering for the subset needed for analysis
  filter(CF1!="No, I do not consent to participate in this survey." ) %>%
  select(GA1_1, GPG5A1_1, IN20_1, IN20_2, INE5_1, #these are the questions concerning child disability
         #director administrator answered GPG5A1_1
         #teachers/assistant teachers answered GA1_1
         A1, A4, AN6,
         TI_1, TI_2...163, TI_2...164, TI_3, TI_4, TI_5, WS4, WS6, #Worker satisfaction for now
         K1_1, K1_2, K1_3, K1_4, K1_5, K1_6, K1_7, K1_8, K1_9, K1_10, #percieved stress scale
    P1,P2_1, P2_2,P2_3, P2_4, P2_5, P2_6, P2_7,P4_1, P4_2, P4_3,P4_4, P4_5, P4_6, P4_7,
         P5_1 ,P5_2,P5_3, P5_4, P5_5, P5_6, P5_7,P11_1,P11_2, P11_3,C2, C2.1,
         A0,CP1a_1, G5_1, G5_2,G5_3, G5_4,G5_5, G5_6,G5_7,
         G51_1, G51_2,G51_3, G51_4,G51_5, G51_6,G51_7,ResponseId, FS6_1, FS6_2, FS6_3, FS6_4, FS6_5, FS6_6, FS6_7, FS6_8, FS6_9, FS6_10, FS6_11, DF1, DF1a, DF2, DF2a, DF3, DF3a, FS1, FS1E, ES7, WS7, ES7a.1, WS8.1, ES7a.2, WS8.2, ES7a.3, WS8.3, ES7a.4, WS8.4, ES7a.5, WS8.5, AN6, AN1, AN3, CP1_1, CP1a_1, CP1b_1, CP1c_1, CP1d_1, CP1e_1, CP1f_1, CP1g_1, CP2_1, CP2a_1, CP2a_2, CP2a_3, CP3_1, CP3a_1, CP3b_1, CP3c_1, CP4_1, CP4a_1, CP4a_2, CP4a_3, CP6_1, CP7_1, CP8,CP9_1, CP10, CP11, CP12, CP13, CP14, ZP2e_1, ZP3e_1, ZP3e_2, `ZP2 _1`, ZP3_1, ZP3_2, A3,
    WS6,
    IN5_8, J1_8, #Mental Health Datapoints
    IN13, IN14 #Behavior Datapoints
         ) %>%
  mutate(
    ####HEAD START
         C2.1_Head = case_when(C2.1=="Not-for-profit agency center" |
                                 C2.1=="Faith-based child care program" |
                                 C2.1=="For-profit center" |
                                 C2.1=="Other center-based" |
                                 C2.1== "School-based" ~ "Other",
                               C2.1=="Head Start or Early Head Start" ~ "HS/EHS",
                               C2.1=="N/A: Home-based"~NA,
                               .default = C2.1),

    ChildNum_Disability = case_when(!is.na(GA1_1) ~ GA1_1,
                                         !is.na(GPG5A1_1) ~ GPG5A1_1,
                                         .default = NA),
         ChildNum_Disability = as.numeric(ChildNum_Disability),
         TerminateNum_ChallengingBehavior = IN20_1,
         LeaveEarlyNum_ChallengingBehavior = IN20_2,
         
         
          Disability_EqualOver20Pct = case_when(
            ChildNum_Disability >= 0.20 ~ "Yes",
            ChildNum_Disability >= 0.20 ~ "No",
            .default = NA),
          
          Disability_Under20Pct = case_when(
            ChildNum_Disability < .20 ~ "Yes",
            ChildNum_Disability >= 0.20 ~ "No",
            .default = NA),
         
          Disability_Pct = case_when(
            ChildNum_Disability > 10 ~ "Over 10%",
            ChildNum_Disability <= 10 ~ "Equal to or Under 10%",
            .default = NA),

          Disability_Pct_Q4 = case_when(
            ChildNum_Disability > 20 ~ "Over 20%",
            ChildNum_Disability <= 4 ~ "Equal to or Under 4%",
            .default = NA),
         
  #Gender
          Staff_Gender = case_when(
            A1=="Female" ~ "Female",
            A1=="Male" ~ "Male",
            !is.na(A1) ~ "Other",
            .default = NA),
                            
    
### Provider Race
        StaffRace_All = case_when(
    A3 == "I prefer not to answer" ~ "I prefer not to answer",  # Keep 'I prefer not to answer' as is
    grepl(",", A3) ~ "Multiple Races",  # If the string contains a comma, mark as 'Multiple Races'
    TRUE ~ A3  # For all other cases, keep the response as is
  ),
        StaffRace_BWH = case_when(StaffRace_All == "White" ~ "White",
                                    StaffRace_All == "I prefer not to answer" ~ NA,
                                  StaffRace_All == "Black or African American" ~ "Black", #there were no hispanic respondents
                                    .default = "Other"),

        HigherEducation = case_when(AN6 == "Some college credit but no degree" |
                                    AN6 == "High school graduate or GED completed" |
                                    AN6 == "Less than high school" ~ "No Advanced Degree",
                                    AN6 == "Graduate/Professional/Doctorate degree" |
                                    AN6 == "Bachelor's degree" |                       
                                    AN6 == "Associate’s degree" ~ "Completed Advanced Degree" ),

#### Mental Health Programs/Services (FS6_10)
      MentalHealthServices_use = case_when(FS6_10 == "Benefit is offered and I HAVE enrolled or used it" ~ "Yes",
                                    is.na(FS6_10)~NA,
                                    .default = "No"),
      MentalHealthServices_know = case_when(FS6_10 == "Benefit is offered and I HAVE enrolled or used it"|
                                   FS6_10=="Benefit is offered but I have NOT enrolled or used it" ~ "Yes",
                                  is.na(FS6_10)~NA,
                                  .default = "No")
)%>%
    mutate( #PSS
    PSS_1 = case_when(K1_1=="Never\n" ~ 0,
                     K1_1=="Almost Never\n" ~ 1,
                     K1_1=="Sometimes\n" ~ 2,
                     K1_1=="Fairly Often\n" ~ 3,
                     K1_1=="Very Often\n" ~ 4,
                     .default = NA),
        PSS_2 = case_when(K1_2=="Never\n" ~ 0,
                     K1_2=="Almost Never\n" ~ 1,
                     K1_2=="Sometimes\n" ~ 2,
                     K1_2=="Fairly Often\n" ~ 3,
                     K1_2=="Very Often\n" ~ 4,
                     .default = NA),
        PSS_3 = case_when(K1_3=="Never\n" ~ 0,
                     K1_3=="Almost Never\n" ~ 1,
                     K1_3=="Sometimes\n" ~ 2,
                     K1_3=="Fairly Often\n" ~ 3,
                     K1_3=="Very Often\n" ~ 4,
                     .default = NA),
        PSS_6 = case_when(K1_6=="Never\n" ~ 0,
                     K1_6=="Almost Never\n" ~ 1,
                     K1_6=="Sometimes\n" ~ 2,
                     K1_6=="Fairly Often\n" ~ 3,
                     K1_6=="Very Often\n" ~ 4,
                     .default = NA),
        PSS_9 = case_when(K1_9=="Never\n" ~ 0,
                     K1_9=="Almost Never\n" ~ 1,
                     K1_9=="Sometimes\n" ~ 2,
                     K1_9=="Fairly Often\n" ~ 3,
                     K1_9=="Very Often\n" ~ 4,
                     .default = NA),
        PSS_10 = case_when(K1_10=="Never\n" ~ 0,
                     K1_10=="Almost Never\n" ~ 1,
                     K1_10=="Sometimes\n" ~ 2,
                     K1_10=="Fairly Often\n" ~ 3,
                     K1_10=="Very Often\n" ~ 4,
                     .default = NA),
       PSS_4 = case_when(K1_4=="Never\n" ~ 4,
                     K1_4=="Almost Never\n" ~ 3,
                     K1_4=="Sometimes\n" ~ 2,
                     K1_4=="Fairly Often\n" ~ 1,
                     K1_4=="Very Often\n" ~ 0,
                     .default = NA),
        PSS_5 = case_when(K1_5=="Never\n" ~ 4,
                     K1_5=="Almost Never\n" ~ 3,
                     K1_5=="Sometimes\n" ~ 2,
                     K1_5=="Fairly Often\n" ~ 1,
                     K1_5=="Very Often\n" ~ 0,
                     .default = NA),
                PSS_7 = case_when(K1_7=="Never\n" ~ 4,
                     K1_7=="Almost Never\n" ~ 3,
                     K1_7=="Sometimes\n" ~ 2,
                     K1_7=="Fairly Often\n" ~ 1,
                     K1_7=="Very Often\n" ~ 0,
                     .default = NA),
        PSS_8 = case_when(K1_8=="Never\n" ~ 4,
                     K1_8=="Almost Never\n" ~ 3,
                     K1_8=="Sometimes\n" ~ 2,
                     K1_8=="Fairly Often\n" ~ 1,
                     K1_8=="Very Often\n" ~ 0,
                    .default = NA),
    PSS_total = PSS_1 + PSS_2 + PSS_3 + PSS_4 + PSS_5 + PSS_6 + PSS_7 + PSS_8 + PSS_9 + PSS_10,
    PSS_binned = cut(PSS_total,
                          breaks = c(-Inf, 13, 26, 40),
                          labels = c("0-13", "14-26", "27-40"),
                          right = TRUE),
    #TI
    JS_1 = case_when(TI_1=="Never" ~ 1,
                     TI_1=="Rarely" ~ 2,
                     TI_1=="Sometimes" ~ 3,
                     TI_1=="Very Often" ~ 4,
                     TI_1=="Always" ~ 5,
                     .default = NA),
    JS_3 = case_when(TI_3=="Never" ~ 1,
                     TI_3=="Rarely" ~ 2,
                     TI_3=="Sometimes" ~ 3,
                     TI_3=="Very Often" ~ 4,
                     TI_3=="Always" ~ 5,
                     .default = NA),
    JS_4 = case_when(TI_4=="Never" ~ 1,
                     TI_4=="Rarely" ~ 2,
                     TI_4=="Sometimes" ~ 3,
                     TI_4=="Very Often" ~ 4,
                     TI_4=="Always" ~ 5,
                     .default = NA),
    JS_2a = case_when(TI_2...163=="Always" ~ 1,
                     TI_2...163=="Ususally" ~ 2,
                     TI_2...163=="About half the time" ~ 3,
                     TI_2...163 =="Seldom" ~ 4,
                     TI_2...163 =="Never" ~ 5,
                     .default = NA),
    JS_2b = case_when(TI_2...164=="Very satisfying" ~ 1,
                     TI_2...164=="Satisfying" ~ 2,
                     TI_2...164=="Neither" ~ 3,
                     TI_2...164 =="Dissatisfying" ~ 4,
                     TI_2...164 =="Totally dissatisfying" ~ 5,
                     .default = NA),
    JS_5 = case_when(TI_5=="Highly unlikely" ~ 1,
                     TI_5=="Unlikely" ~ 2,
                     TI_5=="Somewhat likely" ~ 3,
                     TI_5=="Likely" ~ 4,
                     TI_5=="Highly likely" ~ 5,
                     .default = NA),
  JS_Total = rowSums(cbind(JS_1, JS_3, JS_4, JS_5, JS_2a, JS_2b), na.rm = TRUE),
  JS_binned = cut(JS_Total,
                  breaks = c(6, 14, 22, 30),
                  labels = c("6-14", "15-22", "23-30"),
                  right = TRUE)
        ) %>%
  # Create scores for Health Benefits
  mutate(HealthBenefit_Score = case_when(
    HealthBenefit_use == "Yes" ~ 2,
    HealthBenefit_use == "No" & HealthBenefit_know == "Yes" ~ 1,
    TRUE ~ 0
  ),
  # Create scores for Pension Benefits
  PensionBenefit_Score = case_when(
    PensionBenefit_use == "Yes" ~ 2,
    PensionBenefit_use == "No" & PensionBenefit_know == "Yes" ~ 1,
    TRUE ~ 0
  ),
  # Create scores for Medical Leave
    MedicalLeave_Score = case_when(
    MedicalLeave_use == "Yes" ~ 2,
    MedicalLeave_use == "No" & MedicalLeave_know == "Yes" ~ 1,
    TRUE ~ 0
  ),
  # Create scores for Sick Days
  SickDays_Score = case_when(
    SickDays_use == "Yes" ~ 2,
    SickDays_use == "No" & SickDays_know == "Yes" ~ 1,
    TRUE ~ 0
  ),
  # Create scores for Education Loan Forgiveness
  EdLoanForgiveness_Score = case_when(
    EdLoanForgiveness_use == "Yes" ~ 2,
    EdLoanForgiveness_use == "No" & EdLoanForgiveness_know == "Yes" ~ 1,
    TRUE ~ 0
  ),
  # Create scores for Mental Health Services
  MentalHealthServices_Score = case_when(
    MentalHealthServices_use == "Yes" ~ 2,
    MentalHealthServices_use == "No" & MentalHealthServices_know == "Yes" ~ 1,
    TRUE ~ 0
  ),
  Benefits_Total = rowSums(cbind(HealthBenefit_Score, PensionBenefit_Score, MedicalLeave_Score, SickDays_Score, EdLoanForgiveness_Score, MentalHealthServices_Score), na.rm = TRUE),
  HealthBenefits_Total = rowSums(cbind(MedicalLeave_Score, SickDays_Score, MentalHealthServices_Score), na.rm = TRUE),
  FinBenefits_Total = rowSums(cbind(HealthBenefit_Score, PensionBenefit_Score,EdLoanForgiveness_Score), na.rm = TRUE),
  Benefits_Binned = cut(Benefits_Total,
                  breaks = c(0, 4, 8, 12),
                  labels = c("0-4", "5-8", "9-12"),
                  right = TRUE),
  HealthBenefits_Binned = cut(HealthBenefits_Total,
                  breaks = c(0, 4, 8, 12),
                  labels = c("0-4", "5-8", "9-12"),
                  right = TRUE),
  FinBenefits_Binned = cut(FinBenefits_Total,
                  breaks = c(0, 4, 8, 12),
                  labels = c("0-4", "5-8", "9-12"),
                  right = TRUE)
  ) %>%
  mutate(Gender = case_when(
    A1 == "Male" ~ "Male",
    A1 == "Female" ~ "Female",
    A1 == NA ~ NA,
    TRUE ~ "Other"))

df <- merge(data_clean,weights,by="ResponseId")

# 990 observations didn't have states reported and were dropped in weights, so about 300 aren't matched here in this subset

```

```{r only complete cases}
df_select_1 <- df %>%
    select(A0_FWD, AN6, AN1, A0, Disability_Pct, ChildNum_Disability, C2.1, C2.1_Head, C2.1_Fp, HigherEducation, Gender, A4, FS1, MentalHealthServices_use, MentalHealthServices_know, JS_1, JS_2a, JS_2b, JS_3, JS_4, JS_5, PSS_1, PSS_2, PSS_3, PSS_4, PSS_5, PSS_6, PSS_7, PSS_8, PSS_9, PSS_10, PSS_binned, PSS_total, IN5_8, J1_8, IN13) %>%
   na.omit()

df_select_1 <- df_select_1 %>%
  mutate(Income = case_when(
    AN1 == "$25,000-34,999" ~ 1,
    AN1 == "$35,000-49,999" ~ 2,
    AN1 == "$50,000-74,999" ~ 3,
    AN1 == "≥$75,000" ~ 4,
    AN1 == "I prefer not to answer" ~ NA)) %>%
  mutate(
    MH_1 = case_when(IN5_8=="Yes" ~ 1,
                     IN5_8=="No" ~ 0),
    MH_2 = case_when(J1_8=="Definitely WILL have\n" ~ 1,
                     J1_8=="Unsure\n" ~ 0.5,
                     J1_8=="Definitely WILL NOT have\n" ~ 0),
    MH_3 = case_when(
    MentalHealthServices_use == "Yes" ~ 2,
    MentalHealthServices_use == "No" & MentalHealthServices_know == "Yes" ~ 1,
    TRUE ~ 0
  )) %>%
  mutate(CovidBehavior = case_when(
    IN13 == "None" ~ 0,
    IN13 == "A few" ~ 1,
    IN13 == "About half" ~ 2,
    IN13 == "Most" ~ 3,
    IN13 == "All or nearly all" ~ 4,
    IN13 == "I don't know" ~ NA
  ))

df_select_2 <- df_select_1 %>%
  na.omit()



```

# Descriptive Statistics

## Subgroup Creation

```{r Subgroups}
df_select_2$Disability_Category <- cut(df_select_2$ChildNum_Disability,
                              breaks = c(-Inf, 10.01, Inf),
                              labels = c("Equal to or Under 10%", "Over 10%"),
                              right = FALSE) # This ensures that 10% is included in "10% and under"

# Enhanced histogram plot with ggplot2
ggplot(df_select_2, aes(x = ChildNum_Disability, fill = Disability_Category)) +
  geom_histogram(color = "white", binwidth = 1) + # Use a white borders
  scale_fill_manual(values = c("Equal to or Under 10%" = "salmon", "Over 10%" = "skyblue")) + # Custom colors
  theme_minimal(base_size = 14) + # Use a minimal theme with larger base font size
  theme(
    plot.title = element_text(hjust = 0.5, size = 18, face = "bold"),    # Centered and bold title with larger font
    axis.title = element_text(size = 14, face = "bold"),                 # Bold axis titles with larger font
    axis.text = element_text(size = 12),                                 # Larger axis text
    legend.position = "top"                                              # Position legend on top
  ) +
  labs(title = "Histogram of Number of Children with Disabilities", 
       x = "Percent of Children with Disabilities", 
       y = "Frequency",
       fill = "Disability\nCategory")
# Print summary statistics of ChildNum_Disability
summary_statistics <- summary(df_select_2$ChildNum_Disability)
print(summary_statistics)
```


## Demographic Variables

### Income Breakdown of the sample

```{r}
df_select_2 %>% filter(!is.na(Disability_Pct)) %>% select(AN1, Disability_Pct) %>% tbl_summary(by = Disability_Pct) %>% add_p() %>% add_overall() %>% modify_spanning_header(c("stat_1", "stat_2") ~ "**Disability Percent**")

df_select_2 %>% filter(!is.na(Disability_Pct)) %>% select(Income, Disability_Pct) %>% tbl_summary(by = Disability_Pct) %>% add_p() %>% add_overall() %>% modify_spanning_header(c("stat_1", "stat_2") ~ "**Disability Percent**")

#Sanity Check and Cramer's V
chisq_test <- chisq.test(table(df_select_2$A0_FWD, df_select_2$Disability_Pct))
# Cramer's V for effect size
cramers_v <- cramers_v(chisq_test)
# Print the Cramer's V result
print(cramers_v)


```

### Higher Education Breakdown of the sample

```{r}

df_select_2 %>% filter(!is.na(Disability_Pct)) %>% select(HigherEducation, Disability_Pct) %>% tbl_summary(by = Disability_Pct) %>% add_p() %>% add_overall() %>% modify_spanning_header(c("stat_1", "stat_2") ~ "**Disability Percent**")
```

### Gender Breakdown of the Sample


```{r}
# General Breakdown of the Sample

df_select_2 %>% filter(!is.na(Disability_Pct)) %>% select(Gender, Disability_Pct) %>% tbl_summary(by = Disability_Pct) %>% add_p() %>% add_overall() %>% modify_spanning_header(c("stat_1", "stat_2") ~ "**Disability Percent**")


```

### Racial Breakdown of Sample

```{r}

#StaffRace_BWH calculated separately since not included in model and lowers sample size
# df_select %>% filter(!is.na(Disability_Pct)) %>% select(StaffRace_BWH, Disability_Pct) %>% tbl_summary(by = Disability_Pct) %>% add_p() %>% add_overall() %>% modify_spanning_header(c("stat_1", "stat_2") ~ "**Disability Percent**")

```
### Teacher versus Administrator
```{r teacher/admin profile, echo = FALSE, warning = FALSE}
#A0_FWD

df_select_2 %>% filter(!is.na(Disability_Pct)) %>% select(A0, Disability_Pct) %>% tbl_summary(by = Disability_Pct) %>% add_p() %>% add_overall() %>% modify_spanning_header(c("stat_1", "stat_2") ~ "**Disability Percent**")

chisq_test <- chisq.test(table(df_select_2$A0, df_select_2$Disability_Pct))
# Calculate Cramer's V for effect size
cramers_v <- cramers_v(chisq_test)
print(cramers_v)

```

### Program Type
```{r Program Type, echo = FALSE, warning = FALSE}
df_select_2 %>% filter(!is.na(Disability_Pct)) %>% select(C2.1_Head, Disability_Pct) %>% tbl_summary(by = Disability_Pct) %>% add_p() %>% add_overall() %>% modify_spanning_header(c("stat_1", "stat_2") ~ "**Disability Percent**")

chisq_test <- chisq.test(table(df_select_2$C2.1_Head, df_select_2$Disability_Pct))
# Calculate Cramer's V for effect size
cramers_v <- cramers_v(chisq_test)
print(cramers_v)


```


### Worker Age
```{r Age, echo = FALSE, warning = FALSE}
#A4
df_select_2 %>% filter(!is.na(Disability_Pct)) %>% select(A4, Disability_Pct) %>% tbl_summary(by = Disability_Pct) %>% add_p() %>% add_overall() %>% modify_spanning_header(c("stat_1", "stat_2") ~ "**Disability Percent**")

df_select_2 <- df_select_2 %>% mutate(
  Age_YO = case_when(
    A4 == "18 - 24" |
    A4 == "25 - 34" |
    A4 == "35 - 44" ~ "Under 45",
    A4 == "45 - 54" |
    A4 == "55 - 64" |
    A4 == "75 - 84" |
    A4 == "85 or older" ~ "45 and Over",
    .default = NA)
  )

df_select_2 %>% filter(!is.na(Disability_Pct) & !is.na(Age_YO)) %>% select(Age_YO, Disability_Pct) %>% tbl_summary(by = Disability_Pct) %>% add_p() %>% add_overall() %>% modify_spanning_header(c("stat_1", "stat_2") ~ "**Disability Percent**")

chisq_test <- chisq.test(table(df_select_2$Age_YO, df_select_2$Disability_Pct))
# Calculate Cramer's V for effect size
cramers_v <- cramers_v(chisq_test)
print(cramers_v)

```


## Variables of Interest

### PSS
```{r}
# Use tbl_summary to create a table
table_summary <- df_select_2 %>%
  filter(!is.na(Disability_Pct)) %>%
  select(PSS_binned, Disability_Pct) %>%
  tbl_summary(by = Disability_Pct) %>%
  add_p() %>%
  add_overall() %>%
  modify_spanning_header(c("stat_1", "stat_2") ~ "**Disability Percent**")

# Print the table
print(table_summary)

# Perform chi-squared test
chisq_test <- chisq.test(table(df_select_2$PSS_binned, df_select_2$Disability_Pct))

# Calculate Cramer's V for effect size
cramers_v <- cramers_v(chisq_test)

# Print the Cramer's V result
print(cramers_v)


table_summary <- df_select_2 %>%
  filter(!is.na(Disability_Pct)) %>%
  select(PSS_total, Disability_Pct) %>%
  tbl_summary(by = Disability_Pct) %>%
  add_p() %>%
  add_overall() %>%
  modify_spanning_header(c("stat_1", "stat_2") ~ "**Disability Percent**")

# Print the table
print(table_summary)
# Names of the variables to loop over
pss_vars <- paste0("PSS_", 1:10)  # This creates "PSS_1", "PSS_2", ..., "PSS_10"

# Empty list to store the tbl_summary tables
list_of_tables <- list()

for (var in pss_vars) {
  # Binarize the current PSS variable
  df_select_2 <- df_select_2 %>%
    mutate(!!sym(paste0(var, "_binarized")) := case_when(
      !!sym(var) >= 2 ~ "Equal to or Above 2",
      TRUE ~ "Below 2"
    ))
  
  # Create a table summary for the binarized variable
  table_summary <- df_select_2 %>%
    filter(!is.na(Disability_Pct), !is.na(!!sym(var))) %>%
    select(!!sym(paste0(var, "_binarized")), Disability_Pct) %>%
    tbl_summary(
      by = Disability_Pct,
      statistic = all_categorical() ~ "{n} ({p}%)"
    ) %>%
    add_p() %>%
    add_overall() %>%
    modify_spanning_header(c("stat_1", "stat_2") ~ "**Disability Percent**")

  # Print the table
  print(table_summary)
  
  # Add the table to the list with a named entry for each PSS variable
  list_of_tables[[paste0(var, "_binarized")]] <- table_summary
}

```

### Difficult Behaviors

```{r}

#Stressful class, behaviors
tbl_summary_result <- df_select_2 %>% 
  filter(!is.na(Disability_Pct) & !is.na(IN13)) %>% 
  select(IN13, Disability_Pct) %>% 
  tbl_summary(by = Disability_Pct) %>% 
  add_p() %>% 
  add_overall() %>% 
  modify_spanning_header(c("stat_1", "stat_2") ~ "**Disability Percent**")

# Print the table summary
print(tbl_summary_result)

chisq_test <- chisq.test(table(df_select_2$IN13, df_select_2$Disability_Pct))
# Calculate Cramer's V for effect size
cramers_v <- cramers_v(chisq_test)
# Print the Cramer's V result
print(cramers_v)

# Assuming df_select is your dataset and IN13 is the variable to modify
df_select_2 <- df_select_2 %>%
  mutate(
    IN13_Binary = case_when(
      IN13 %in% c("A few", "None") ~ "Less than half",
      IN13 %in% c("Most", "All or nearly all", "About half") ~ "Half or more",
      IN13 %in% c("I don't know") ~ "I don't know",
      TRUE ~ NA_character_  # Handle "I don’t know" or any unexpected values as NA
    )
  )

# Create a summary table grouped by Disability_Pct
tbl_summary_result <- df_select_2 %>%
  filter(!is.na(Disability_Pct) & !is.na(IN13_Binary)) %>%  # Ensure no NA values in key columns
  select(IN13_Binary, Disability_Pct) %>%
  tbl_summary(
    by = Disability_Pct,  # Group by Disability Percent
    statistic = all_categorical() ~ "{n} / {N} ({p}%)"
  ) %>%
  add_p() %>%
  add_overall() %>%
  modify_spanning_header(c("stat_1", "stat_2") ~ "**Disability Percent**")

# Print the table summary
print(tbl_summary_result)

```

### Mental Health Resources

```{r}
df_select_2 %>% filter(!is.na(Disability_Pct)) %>% select(IN5_8, Disability_Pct) %>% tbl_summary(by = Disability_Pct) %>% add_p() %>% add_overall() %>% modify_spanning_header(c("stat_1", "stat_2") ~ "**Disability Percent**")

chisq_test <- chisq.test(table(df$IN5_8, df$Disability_Pct))
# Calculate Cramer's V for effect size
cramers_v <- cramers_v(chisq_test)
# Print the Cramer's V result
print(cramers_v)

```

```{r}
df_select_2 %>% filter(!is.na(Disability_Pct)) %>% select(J1_8, Disability_Pct) %>% tbl_summary(by = Disability_Pct) %>% add_p() %>% add_overall() %>% modify_spanning_header(c("stat_1", "stat_2") ~ "**Disability Percent**")

chisq_test <- chisq.test(table(df_select$J1_8, df_select$Disability_Pct))
# Calculate Cramer's V for effect size
cramers_v <- cramers_v(chisq_test)

```

```{r}
# Use tbl_summary to create a table
table_summary <- df_select_2 %>%
  filter(!is.na(Disability_Pct), !is.na(MH_3)) %>%
  select(MH_3, Disability_Pct) %>%
  tbl_summary(by = Disability_Pct) %>%
  add_p() %>%
  add_overall() %>%
  modify_spanning_header(c("stat_1", "stat_2") ~ "**Disability Percent**")

# Print the table
print(table_summary)

```


### Turnover Intentions

```{r}
df_select_2 <- df_select_2 %>% mutate(
  JS_Total = rowSums(cbind(JS_1, JS_3, JS_4, JS_5, JS_2a, JS_2b), na.rm = TRUE),
  JS_binned = cut(JS_Total,
                  breaks = c(6, 14, 22, 30),
                  labels = c("6-14", "15-22", "23-30"),
                  right = TRUE)
        )

# Use tbl_summary to create a table
table_summary <- df_select_2 %>%
  filter(!is.na(Disability_Pct), !is.na(JS_binned)) %>%
  select(JS_binned, Disability_Pct) %>%
  tbl_summary(by = Disability_Pct) %>%
  add_p() %>%
  add_overall() %>%
  modify_spanning_header(c("stat_1", "stat_2") ~ "**Disability Percent**")

# Print the table
print(table_summary)

# Perform chi-squared test
chisq_test <- chisq.test(table(df_select_2$JS_binned, df_select_2$Disability_Pct))

# Calculate Cramer's V for effect size
cramers_v <- cramers_v(chisq_test)

# Print the Cramer's V result
print(cramers_v)
# Binarize the JS_1 variable
df_select_2 <- df_select_2 %>%
  mutate(JS_1_binarized = case_when(
    JS_1 > 3 ~ "Above 3",
    TRUE ~ "3 or Below"
  ))

# Create a table summary for the binarized JS_1 variable
table_summary <- df_select_2 %>%
  filter(!is.na(Disability_Pct), !is.na(JS_1)) %>%
  select(JS_1_binarized, Disability_Pct) %>%
  tbl_summary(
    by = Disability_Pct,
    statistic = all_categorical() ~ "{n} ({p}%)"
  ) %>%
  add_p() %>%
  add_overall() %>%
  modify_spanning_header(c("stat_1", "stat_2") ~ "**Disability Percent**")

# Print the table
print(table_summary)

df_select_2 <- df_select_2 %>%
  mutate(JS_2_binarized = case_when(
    JS_2a > 3 ~ "Above 3",
    TRUE ~ "3 or Below"
  ))

# Create a table summary for the binarized JS_1 variable
table_summary <- df_select_2 %>%
  filter(!is.na(Disability_Pct), !is.na(JS_2a)) %>%
  select(JS_2_binarized, Disability_Pct) %>%
  tbl_summary(
    by = Disability_Pct,
    statistic = all_categorical() ~ "{n} ({p}%)"
  ) %>%
  add_p() %>%
  add_overall() %>%
  modify_spanning_header(c("stat_1", "stat_2") ~ "**Disability Percent**")

# Print the table
print(table_summary)

df_select_2 <- df_select_2 %>%
  mutate(JS_3_binarized = case_when(
    JS_2b > 3 ~ "Above 3",
    TRUE ~ "3 or Below"
  ))

# Create a table summary for the binarized JS_1 variable
table_summary <- df_select_2 %>%
  filter(!is.na(Disability_Pct), !is.na(JS_2b)) %>%
  select(JS_3_binarized, Disability_Pct) %>%
  tbl_summary(
    by = Disability_Pct,
    statistic = all_categorical() ~ "{n} ({p}%)"
  ) %>%
  add_p() %>%
  add_overall() %>%
  modify_spanning_header(c("stat_1", "stat_2") ~ "**Disability Percent**")

# Print the table
print(table_summary)

df_select_2 <- df_select_2 %>%
  mutate(JS_4_binarized = case_when(
    JS_3 > 3 ~ "Above 3",
    TRUE ~ "3 or Below"
  ))

# Create a table summary for the binarized JS_1 variable
table_summary <- df_select_2 %>%
  filter(!is.na(Disability_Pct), !is.na(JS_3)) %>%
  select(JS_4_binarized, Disability_Pct) %>%
  tbl_summary(
    by = Disability_Pct,
    statistic = all_categorical() ~ "{n} ({p}%)"
  ) %>%
  add_p() %>%
  add_overall() %>%
  modify_spanning_header(c("stat_1", "stat_2") ~ "**Disability Percent**")

# Print the table
print(table_summary)

df_select_2 <- df_select_2 %>%
  mutate(JS_5_binarized = case_when(
    JS_4 > 3 ~ "Above 3",
    TRUE ~ "3 or Below"
  ))

# Create a table summary for the binarized JS_1 variable
table_summary <- df_select_2 %>%
  filter(!is.na(Disability_Pct), !is.na(JS_4)) %>%
  select(JS_5_binarized, Disability_Pct) %>%
  tbl_summary(
    by = Disability_Pct,
    statistic = all_categorical() ~ "{n} ({p}%)"
  ) %>%
  add_p() %>%
  add_overall() %>%
  modify_spanning_header(c("stat_1", "stat_2") ~ "**Disability Percent**")

# Print the table
print(table_summary)

df_select_2 <- df_select_2 %>%
  mutate(JS_6_binarized = case_when(
    JS_5 > 3 ~ "Above 3",
    TRUE ~ "3 or Below"
  ))

# Create a table summary for the binarized JS_1 variable
table_summary <- df_select_2 %>%
  filter(!is.na(Disability_Pct), !is.na(JS_5)) %>%
  select(JS_6_binarized, Disability_Pct) %>%
  tbl_summary(
    by = Disability_Pct,
    statistic = all_categorical() ~ "{n} ({p}%)"
  ) %>%
  add_p() %>%
  add_overall() %>%
  modify_spanning_header(c("stat_1", "stat_2") ~ "**Disability Percent**")

# Print the table
print(table_summary)
```

## Chronbach Alpha 

### PSS

```{r}
# Select only the PSS variables for Cronbach's alpha calculation
pss_data <- df_select_2 %>% select(PSS_1, PSS_2, PSS_3, PSS_4, PSS_5, PSS_6, PSS_7, PSS_8, PSS_9, PSS_10)

# Calculate Cronbach's alpha
alpha_result <- alpha(pss_data)

# Print the overall Cronbach's alpha result
print(alpha_result$total$raw_alpha)

```

### Mental Health Resources

```{r}
MH_data <- df_select_2 %>% select(MH_1, MH_2, MH_3)

# Calculate Cronbach's alpha
alpha_result <- alpha(MH_data)

# Print the overall Cronbach's alpha result
print(alpha_result$total$raw_alpha)

```

### Turnover Intentions

```{r}

TI_data <- df_select_2 %>% select(JS_1, JS_3, JS_4, JS_2a, JS_2b, JS_5)

# Calculate Cronbach's alpha
alpha_result <- alpha(TI_data)

# Print the overall Cronbach's alpha result
print(alpha_result$total$raw_alpha)

```


## CFA

```{r}
#CFA
# Define the CFA model (same as before)
cfa_model <- '
  PSS =~ PSS_1 + PSS_2 + PSS_3 + PSS_4 + PSS_5 + PSS_6 + PSS_7 + PSS_8 + PSS_9 + PSS_10
  MHResources =~ MH_1 + MH_2 + MH_3
  TurnoverIntention =~ JS_1 + JS_2a + JS_2b + JS_3 + JS_4 + JS_5
'

# Fit the two-group CFA model
cfa_fit_two_group <- cfa(model = cfa_model, data = df_select_2, group = "Disability_Pct", estimator = "MLR")

# Summary of the two-group fit
summary(cfa_fit_two_group, fit.measures = TRUE, standardized = TRUE)

# Check model fit measures
fitMeasures(cfa_fit_two_group)

# Standardized loadings for both groups
standardizedSolution(cfa_fit_two_group)

# Unstandardized loadings for both groups
parameterEstimates(cfa_fit_two_group)


# Extract specific fit indices
fit_indices <- fitMeasures(cfa_fit_two_group, c("rmsea", "srmr", "cfi", "tli"))

# Print the extracted fit indices
print(fit_indices)


```

## SEM

### Basic Model
```{r}
model <- '
  # Latent variables definitions
  PSS =~ PSS_1 + PSS_2 + PSS_3 + PSS_4 + PSS_5 + PSS_6 + PSS_7 + PSS_8 + PSS_9 + PSS_10
  MHResources =~ MH_1 + MH_2 + MH_3
  TurnoverIntention =~ JS_1 + JS_2a + JS_2b + JS_3 + JS_4 + JS_5

  # Regressions
  TurnoverIntention ~ MHResources + PSS + CovidBehavior + A0 + AN6 + C2.1 + Income
'

# Fit the multi-group SEM
fit <- sem(model, data = df_select_2, group = "Disability_Pct")
summary(fit)

# Optionally, visualize the path diagram for each group
semPaths(fit, whatLabels="est", layout="tree", rotation=2)

# Extract fit measures for each group
fitMeasures(fit, c("cfi", "rmsea", "srmr", "tli"))

```

### Mediation Model

```{r}
model <- '
  # Latent variables definitions
  PSS =~ PSS_1 + PSS_2 + PSS_3 + PSS_4 + PSS_5 + PSS_6 + PSS_7 + PSS_8 + PSS_9 + PSS_10
  MHResources =~ MH_1 + MH_2 + MH_3
  TurnoverIntention =~ JS_1 + JS_2a + JS_2b + JS_3 + JS_4 + JS_5

  # Direct paths
  TurnoverIntention ~ MHResources + PSS + CovidBehavior + A0 + AN6 + C2.1 + Income
  MHResources ~ PSS
  CovidBehavior ~ PSS
  
  # Mediation paths: specifying indirect effects
  # Note: Indirect effects are implicit in SEM and calculated from the product of direct paths
  # No need to specify interaction terms unless modeling moderation
'

fit <- sem(model, data = df_select_2, group = "Disability_Pct")
summary(fit, standardized = TRUE, rsquare = TRUE)

# Optionally, visualize the path diagram for each group
semPaths(fit, whatLabels="est", layout="tree", rotation=2)

# Extract fit measures for each group
fitMeasures(fit, c("cfi", "rmsea", "srmr", "tli"))
```


## Meaasurement Invariance

```{r}
model <- '
  # Latent variables definitions
  PSS =~ PSS_1 + PSS_2 + PSS_3 + PSS_4 + PSS_5 + PSS_6 + PSS_7 + PSS_8 + PSS_9 + PSS_10
  MHResources =~ MH_1 + MH_2 + MH_3
  TurnoverIntention =~ JS_1 + JS_2a + JS_2b + JS_3 + JS_4 + JS_5

  # Direct paths
  TurnoverIntention ~ MHResources + PSS + CovidBehavior + A0 + AN6 + C2.1 + Income
  MHResources ~ PSS
  CovidBehavior ~ PSS
  
  # Mediation paths: specifying indirect effects
  # Note: Indirect effects are implicit in SEM and calculated from the product of direct paths
  # No need to specify interaction terms unless modeling moderation
'

fit <- sem(model, data = df_select_2, group = "Disability_Pct")
summary(fit, standardized = TRUE, rsquare = TRUE)

# Optionally, visualize the path diagram for each group
semPaths(fit, whatLabels="est", layout="tree", rotation=2)

# Extract fit measures for each group
fitMeasures(fit, c("cfi", "rmsea", "srmr", "tli"))


model2 <- '
  # Latent variables definitions
  PSS =~ a*PSS_1 + b*PSS_2 + c*PSS_3 + d*PSS_4 + e*PSS_5 + f*PSS_6 + g*PSS_7 + h*PSS_8 + i*PSS_9 + j*PSS_10
  MHResources =~ k*MH_1 + l*MH_2 + m*MH_3
  TurnoverIntention =~ n*JS_1 + o*JS_2a + p*JS_2b + q*JS_3 + r*JS_4 + s*JS_5

  # Direct paths
  TurnoverIntention ~ MHResources + PSS + CovidBehavior + A0 + AN6 + C2.1 + Income
  MHResources ~ PSS
  CovidBehavior ~ PSS
  
  # Mediation paths: specifying indirect effects
  # Note: Indirect effects are implicit in SEM and calculated from the product of direct paths
  # No need to specify interaction terms unless modeling moderation
'

fit2 <- sem(model2, data = df_select_2, group = "Disability_Pct")
summary(fit2, standardized = TRUE, rsquare = TRUE)

# Optionally, visualize the path diagram for each group
semPaths(fit2, whatLabels="est", layout="tree", rotation=2)

# Extract fit measures for each group

fitMeasures(fit, c("cfi", "rmsea", "srmr", "tli"))

# Perform chi-square difference test
chi_diff_test <- lavTestLRT(fit2, fit)

# Output the results of the chi-square difference test
print(chi_diff_test)


```

## Comparing the Two Groups

```{r}

# Define the SEM model (replace with your actual model specification)
model_unconstrained <- '
  # Latent variables definitions
  PSS =~ PSS_1 + PSS_2 + PSS_3 + PSS_4 + PSS_5 + PSS_6 + PSS_7 + PSS_8 + PSS_9 + PSS_10
  MHResources =~ MH_1 + MH_2 + MH_3
  TurnoverIntention =~ JS_1 + JS_2a + JS_2b + JS_3 + JS_4 + JS_5
  TurnoverIntention ~ MHResources + PSS + CovidBehavior + A0 + AN6 + C2.1 + Income
    MHResources ~ PSS
  CovidBehavior ~ PSS
'

# Fit the unconstrained multi-group SEM
fit_unconstrained <- sem(model_unconstrained, data = df_select_2, group = "Disability_Pct")

# Define the constrained model (imposing equality constraints on all parameters)
model_constrained <- '
  # Applying equality constraints across groups for all parameters
  PSS =~ PSS_1 + PSS_2 + PSS_3 + PSS_4 + PSS_5 + PSS_6 + PSS_7 + PSS_8 + PSS_9 + PSS_10
  MHResources =~ MH_1 + MH_2 + MH_3
  TurnoverIntention =~ JS_1 + JS_2a + JS_2b + JS_3 + JS_4 + JS_5
  TurnoverIntention ~ a*MHResources + b*PSS + c*CovidBehavior + A0 + AN6 + C2.1 + Income
  MHResources ~ h*PSS
  CovidBehavior ~ i*PSS
'

# Fit the constrained multi-group SEM
fit_constrained <- sem(model_constrained, data = df_select_2, group = "Disability_Pct")
summary(fit_unconstrained)
summary(fit_constrained)

# Perform chi-square difference test
chi_diff_test <- lavTestLRT(fit_unconstrained, fit_constrained)

# Output the results of the chi-square difference test
print(chi_diff_test)

```

## Missingness Analysis

```{r}
library(naniar)
library(mice)

df_select_2_full <- df %>%
    select(A0_FWD, AN6, AN1, A0, Disability_Pct, ChildNum_Disability, C2.1, C2.1_Head, C2.1_Fp, HigherEducation, Gender, A4, FS1, MentalHealthServices_use, MentalHealthServices_know, JS_1, JS_2a, JS_2b, JS_3, JS_4, JS_5, PSS_1, PSS_2, PSS_3, PSS_4, PSS_5, PSS_6, PSS_7, PSS_8, PSS_9, PSS_10, PSS_binned, PSS_total, IN5_8, J1_8, IN13) %>%
   na.omit()


#Scale
vis_miss(df_select_2_full)

summary(is.na(df))

# Analyze missingness of Disability_Pct by different values of A0
missingness_by_A0 <- df %>%
  group_by(A0) %>%
  summarise(
    Total = n(),
    Missing_Disability_Pct = sum(is.na(Disability_Pct)),
    Proportion_Missing = Missing_Disability_Pct / Total
  )

# View the result
print(missingness_by_A0)

# Analyze missingness of Disability_Pct by different values of A0
missingness_by_CP <- df %>%
  group_by(C2.1_Head) %>%
  summarise(
    Total = n(),
    Missing_Disability_Pct = sum(is.na(Disability_Pct)),
    Proportion_Missing = Missing_Disability_Pct / Total
  )

# View the result
print(missingness_by_CP)

# Analyze missingness of Disability_Pct by different values of A0
missingness_by_Race <- df %>%
  group_by(StaffRace_BWH) %>%
  summarise(
    Total = n(),
    Missing_Disability_Pct = sum(is.na(Disability_Pct)),
    Proportion_Missing = Missing_Disability_Pct / Total
  )

# View the result
print(missingness_by_Race)

# Analyze missingness of Disability_Pct by different values of A0
missingness_by_Inc <- df %>%
  group_by(AN1) %>%
  summarise(
    Total = n(),
    Missing_Disability_Pct = sum(is.na(Disability_Pct)),
    Proportion_Missing = Missing_Disability_Pct / Total
  )

# View the result
print(missingness_by_Inc)

# Analyze missingness of Disability_Pct by different values of A0
missingness_by_Age <- df %>%
  group_by(A4) %>%
  summarise(
    Total = n(),
    Missing_Disability_Pct = sum(is.na(Disability_Pct)),
    Proportion_Missing = Missing_Disability_Pct / Total
  )

# View the result
print(missingness_by_Age)

# Print the result for A0
kable(missingness_by_A0, caption = "Missingness of Disability Percentage by Job")

# Print the result for C2.1_Head
kable(missingness_by_CP, caption = "Missingness of Disability Percentage by Program")

# Print the result for StaffRace_BWH
kable(missingness_by_Race, caption = "Missingness of Disability Percentage by Staff Race")

# Print the result for AN1
kable(missingness_by_Inc, caption = "Missingness of Disability Percentage by Income")

# Print the result for A4
kable(missingness_by_Age, caption = "Missingness of Disability Percentage by Age")

```
```
